\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-08-14 paper.qmd
Changed the point color to black

trimesh_removed_pbmc <- vis_rmlg_mesh(
  distance_edges = distance_pbmc,
  benchmark_value = benchmark_pbmc,
  tr_coord_df = tr_from_to_df_pbmc,
  distance_col = "distance") +
  #xlim(sc_xlims) + ylim(sc_ylims) +
  interior_annotation("a", sc_ltr_pos)

@@

trimesh_removed_pbmc <- vis_rmlg_mesh(
  distance_edges = distance_pbmc,
  benchmark_value = benchmark_pbmc,
  tr_coord_df = tr_from_to_df_pbmc,
  distance_col = "distance") +
  geom_point(
    data = tsne_pbmc_scaled,
    aes(
      x = tSNE1,
      y = tSNE2
    ),
    alpha = 0.3,
    size = 0.1,
    color = "#000000"
  ) +
  theme_void() #+
  #xlim(sc_xlims) + ylim(sc_ylims) +
  #interior_annotation("a", sc_ltr_pos)

@@

proj1_pbmc_tsne <- gen_proj_langevitour(
  points_df = df_exe,
  projection = projection,
  edge_df = distance_df_small_edges |> select(-distance)
) + 
  theme_void() + 
  theme(legend.position = "none")

@@

proj2_pbmc_tsne <- gen_proj_langevitour(
  points_df = df_exe,
  projection = projection,
  edge_df = distance_df_small_edges |> select(-distance)
) + 
  theme_void() + 
  theme(legend.position = "none")

@@

proj3_pbmc_tsne <- gen_proj_langevitour(
  points_df = df_exe,
  projection = projection,
  edge_df = distance_df_small_edges |> select(-distance)
) + 
  theme_void() + 
  theme(legend.position = "none")

@@

```{r}
#| echo: false
#| fig-cap: "Model in $2\\text{-}D$, on the tSNE layout, and three views of the fit in projections from $9\text{-}D$, for the PBMC3k data ($(s_1, \ s_2) = (-0.050, \ -0.058)$, $b = 300 \  (15, \ 20)$, $m = 136$, benchmark value to remove large edges is $0.133$). (The **langevitour** software is used to view the data with a tour, and the full video is available at <https://youtu.be/5Y1hE4i7N2k>)."
#| label: fig-pbmc2-sc
#| fig-pos: H
#| out-height: 100%
#| eval: false

@@

::: {#fig-pbmc2-sc layout-ncol="2" fig-pos="H"}
![](figures/pbmc3k/tsne_trimesh_plot.png)

![](figures/pbmc3k/sc_4.png)

![](figures/pbmc3k/sc_5.png)

![](figures/pbmc3k/sc_6.png)

Model in \gD{}, on the tSNE layout, and three views of the fit in projections from $9\text{-}D$, for the PBMC3k data ($(s_1, \ s_2) = (-0.050, \ -0.058)$, $b = 300 \  (15, \ 20)$, $m = 136$, benchmark value to remove large edges is $0.133$). (The **langevitour** software is used to view the data with a tour, and the full video is available at <https://youtu.be/5Y1hE4i7N2k>).
:::

>>>>

trimesh_removed_pbmc <- vis_rmlg_mesh(
  distance_edges = distance_pbmc,
  benchmark_value = benchmark_pbmc,
  tr_coord_df = tr_from_to_df_pbmc,
  distance_col = "distance") +
  geom_point(
    data = umap_pbmc_scaled,
    aes(
      x = UMAP1,
      y = UMAP2
    ),
    alpha = 0.3,
    size = 0.1,
    color = "#000000"
  )

@@

trimesh_removed_pbmc <- vis_rmlg_mesh(
  distance_edges = distance_pbmc,
  benchmark_value = benchmark_pbmc,
  tr_coord_df = tr_from_to_df_pbmc,
  distance_col = "distance") +
  geom_point(
    data = tsne_pbmc_scaled,
    aes(
      x = tSNE1,
      y = tSNE2
    ),
    alpha = 0.2,
    color = "#000000"
  ) 
  #xlim(sc_xlims) + ylim(sc_ylims) +
  #interior_annotation("a", sc_ltr_pos)

@@

proj1_pbmc_tsne <- gen_proj_langevitour(
  points_df = df_exe,
  projection = projection,
  edge_df = distance_df_small_edges |> select(-distance)
)

@@

proj2_pbmc_tsne <- gen_proj_langevitour(
  points_df = df_exe,
  projection = projection,
  edge_df = distance_df_small_edges |> select(-distance)
)

@@

proj3_pbmc_tsne <- gen_proj_langevitour(
  points_df = df_exe,
  projection = projection,
  edge_df = distance_df_small_edges |> select(-distance)
)

@@

```{r}
#| echo: false
#| fig-cap: "Model in $2\\text{-}D$, on the tSNE layout, and three views of the fit in projections from $9\text{-}D$, for the PBMC3k data ($(s_1, \ s_2) = (-0.050, \ -0.058)$, $b = 300 \  (15, \ 20)$, $m = 136$, benchmark value to remove large edges is $0.133$). (The **langevitour** software is used to view the data with a tour, and the full video is available at <https://youtu.be/5Y1hE4i7N2k>)."
#| label: fig-pbmc2-sc
#| fig-pos: H
#| out-height: 100%
#| eval: true

@@

<!-- ::: {#fig-pbmc2-sc layout-ncol="2" fig-pos="H"} -->
<!-- ![](figures/pbmc3k/tsne_trimesh_plot.png) -->

<!-- ![](figures/pbmc3k/sc_4.png) -->

<!-- ![](figures/pbmc3k/sc_5.png) -->

<!-- ![](figures/pbmc3k/sc_6.png) -->

<!-- Model in \gD{}, on the tSNE layout, and three views of the fit in projections from $9\text{-}D$, for the PBMC3k data ($(s_1, \ s_2) = (-0.050, \ -0.058)$, $b = 300 \  (15, \ 20)$, $m = 136$, benchmark value to remove large edges is $0.133$). (The **langevitour** software is used to view the data with a tour, and the full video is available at <https://youtu.be/5Y1hE4i7N2k>). -->
<!-- ::: -->

### 2024-08-14 paper.tex
Added trimesh of PaCMAP
Changed the point color to black

\begin{minipage}{0.50\linewidth}
\includegraphics{figures/pbmc3k/tsne_trimesh_plot.png}\end{minipage}%
%
\begin{minipage}{0.50\linewidth}
\includegraphics{figures/pbmc3k/sc_4.png}\end{minipage}%
\newline
\begin{minipage}{0.50\linewidth}
\includegraphics{figures/pbmc3k/sc_5.png}\end{minipage}%
%
\begin{minipage}{0.50\linewidth}
\includegraphics{figures/pbmc3k/sc_6.png}\end{minipage}%

\caption{\label{fig-pbmc2-sc}Model in \gD{}, on the tSNE layout, and
three views of the fit in projections from \(9\text{-}D\), for the
PBMC3k data (\((s_1, \ s_2) = (-0.050, \ -0.058)\),
\(b = 300 \  (15, \ 20)\), \(m = 136\), benchmark value to remove large
edges is \(0.133\)). (The \textbf{langevitour} software is used to view
the data with a tour, and the full video is available at
\url{https://youtu.be/5Y1hE4i7N2k}).}

@@

>>>>

\includegraphics[width=1\textwidth,height=1\textheight]{paper_files/figure-pdf/fig-pbmc2-sc-1.pdf}

\caption{\label{fig-pbmc2-sc}Model in \(2\text{-}D\), on the tSNE
layout, and three views of the fit in projections from \(9  ext{-}D\),
for the PBMC3k data (\((s_1,  s_2) = (-0.050,  -0.058)\),
\(b = 300   (15,  20)\), \(m = 136\), benchmark value to remove large
edges is \(0.133\)). (The \textbf{langevitour} software is used to view
the data with a tour, and the full video is available at
\url{https://youtu.be/5Y1hE4i7N2k}).}

@@

\begin{center}
\includegraphics[width=1\textwidth,height=\textheight]{paper_files/figure-pdf/unnamed-chunk-52-1.pdf}
\end{center}
